---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ".",
  fig.path = "man/figures/README-",
  out.width = "100%" , message = FALSE
)
```

# mread.yaml

<!-- badges: start -->
<!-- badges: end -->

mread.yaml provides alternate model specification formats, primarily based 
on yaml. 

## Installation

``` r
# install.packages("devtools")
devtools::install_github("kylebaron/mread.yaml")
```


## Example

### Setup


```{r}
library(mread.yaml)
library(dplyr)
library(mrgsolve)
```


Read some input code
```{r}
examp <- system.file("examples", "two_cmt_model.cpp", package = "mread.yaml")
```


This looks identical to the regular model specification file, but rather than 
writing differential equations, we write the model in reaction notation.  
```{yaml,eval=FALSE, code = readLines(examp)}
```

In this simple example, we write the model as a series of fluxes:

- absorption from the gut to the central compartment (1)
- elimination (2)
- transfer between the central and peripheral compartments (3)

mread.yaml provides a function to read and parse this type of model specification
file and return a model object just like [mrgsolve::mread].

```{r example}
mod <- mread_rxn(examp, delta = 0.1, end = 48)
```

Once the model is loaded, it functions just like you had written it using ODEs

```{r}
mod
```

```{r}
mrgsim(mod, ev(amt = 100)) %>% plot
```


In fact, all `mread_rxn()` does, is parse the reactions and write that math 
as ODEs

```{c, eval=FALSE, code = mod@code}

```

